Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2016-02-02 GECCO/volunteer-clouds-gecco16.tex
Back to 8 pages
Revised structure of the main section
To make it a single section of experiments with subsections. Also revises intro and thus closes #97 if nobody else has anything to say.

\title{Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources 
for Low Cost Distributed Evolutionary Computation }
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

So, the rest of the paper is organized as follows: Next we present the
state of the art in web-based distributed
computational systems along with attempts to predict and model its
behavior  in Section \ref{sec:soa}. The first results in a volunteer
setting are described 
in Section \ref{sec:exp1}, and experiments using a new client
architecture that uses web workers in Section \ref{sec:w2} and then
applied to a different problem in Section \ref{sec:rastrigin}. 
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.

@@

JavaScript can be used either for unwitting, that is, stealth,
\cite{unwitting-ec} or volunteer 
\cite{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\cite{duda2013distributed,DBLP:journals/corr/abs-0801-1210} 
that even
used the client's GPU \cite{duda2013gpu}. 
%Also a bit out of scope. Have to reduce the paper. 
% Even if, as said above, Java
% is not the best option, many other researchers have
% used Java \cite{chong:1999:jDGPi} and others have gone away from the
% server-based paradigm to embrace peer to peer systems
% \cite{jin2006constructing,10.1109/ICICSE.2008.99,DBLP:conf/3pgcic/GuervosMFEL12}. These
% computing 
% platforms avoid single points of failure (the server) but, since they
% need a certain amount of infrastructure installed to start, the
% threshold to join them is much higher. % (Paloma) Do yo
                                % mean... higher? A low threshold
                                % means that is easy to happen
                                % something.
%Correct. But maybe in this new version we should eliminate this
%paragraph altogether. 
% The next paragraph has been suppresed.

@@

\section{Experimental results}
\label{sec:exp1}

@@

We set up different experiments by deploying the server in a cloud
service, which changed in every one. This server runs a web service
which stores chromosomes sent from clients and sends them back. It is
an open source system that has been described extensively in
\cite{2016arXiv160101607Manom}. The client runs an evolutionary
algorithm written in JavaScript, that after a number of generations
sends back the best individual to the server, requesting at the same
time a random individual of those stored in the server. The experiment
starts by setting up a website that is sent by the server and announcing it on several social
networks so that people contribute to them by going to the page and
staying there for a while.

@@

The results reported above indicated that we should look for a way of
increasing the time that every user devotes. This led us to create an
architecture that uses Web Workers, which is described in
\cite{2016arXiv160101607Manom}; web workers work in the background even if
the web page is not in focus. A few improvements were also tested,
basically using a random population and restarting the web worker when
the solution was found.

@@

\section{Working on a hard optimization problem}
\label{sec:rastrigin}

>>>>

\title{Performance for the masses: Experiments with A Web Based Architecture to Harness Volunteer Resources 
for Low Cost Distributed Evolutionary Computation}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

@@

So, the rest of the paper is organized as follows: Next we present the
state of the art in web-based distributed
computational systems along with attempts to predict and model its
behavior  in Section \ref{sec:soa}. A brief presentation of the
methodology used and the results of the experiments are presented in
Section \ref{sec:exp1}, including new results using web workers on the
same problem and on a new problem, Rastrigin's or F15 function. 
Finally, conclusions and future lines of work are presented in Section
\ref{sec:conclusion}.

@@

JavaScript can be used either for unwitting, that is, stealth,
\cite{unwitting-ec} or volunteer 
\cite{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\cite{duda2013distributed,DBLP:journals/corr/abs-0801-1210}

% that even
% used the client's GPU \cite{duda2013gpu}. 
%Also a bit out of scope. Have to reduce the paper. 
% Even if, as said above, Java
% is not the best option, many other researchers have
% used Java \cite{chong:1999:jDGPi} and others have gone away from the
% server-based paradigm to embrace peer to peer systems
% \cite{jin2006constructing,10.1109/ICICSE.2008.99,DBLP:conf/3pgcic/GuervosMFEL12}. These
% computing 
% platforms avoid single points of failure (the server) but, since they
% need a certain amount of infrastructure installed to start, the
% threshold to join them is much higher. % (Paloma) Do yo
                                % mean... higher? A low threshold
                                % means that is easy to happen
                                % something.
%Correct. But maybe in this new version we should eliminate this
%paragraph altogether. 
% The next paragraph has been suppresed.

@@

\section{Methodology and experimental results}
\label{sec:exp1}

@@

We set up different experiments by deploying the server in free cloud
services, changing it from one experiment to the next if needed. This server runs a web service
which stores chromosomes sent from clients and serves requests to
them; it is 
an open source system that has been described extensively in
\cite{2016arXiv160101607Manom}. The client runs an evolutionary
algorithm written in JavaScript, that after a number of generations
sends back the best individual to the server, requesting at the same
time a random individual of those stored in the server. The experiment
starts by setting up a website that is sent by the server and announcing it on several social
networks so that people contribute to them by going to the page and
staying there for a while.

@@

The results reported above indicated that we should look for a way of
increasing the time users spend on the page. This led us to create an
architecture that uses Web Workers, which is described in
\cite{2016arXiv160101607Manom}; web workers work in the background even if
the web page is not in focus. A few improvements were also tested,
basically using a random population and restarting the web worker when
the solution was found.

@@

\subsection{A hard optimization problem: Rastrigin's function}
\label{sec:rastrigin}
